---
title: "Assignment 4"
author: "Ben Merz"
date: "2023-01-17"
output: 
 prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# Working with matrices, lists, and data frames

1. Assign to the variable n_dims a single random integer between 3 and 10.
  + Create a vector of consecutive integers from 1 to n_dims2.
  
```{r}
set.seed(100)
n_dims = sample(3:10, 1)
myVec = c(1:(n_dims)^2)
print(myVec)
```
  + Use the sample function to randomly reshuffle these values.
```{r}
rVec <- sample(myVec)
print(rVec)
```
  + create a square matrix with these elements.
```{r}
mMat <- matrix(data=rVec, nrow=n_dims, ncol=n_dims)
print(mMat)
```
  + find a function in r to transpose the matrix.
```{r}
tmMat <- t(mMat)
print(tmMat)
```
  + calculate the sum and the mean of the elements in the first row and then the last row.
```{r}
# first row
mean(tmMat[1,])
sum(tmMat[1,])

# last row
mean(tmMat[n_dims,])
sum(tmMat[n_dims,])
```
2. Create a list with the following named elements:
```{r}
my_matrix = matrix(data = runif(16), nrow = 4, ncol = 4)

```









