---
title: "Assignment 4 and 5"
author: "Ben Merz"
date: "2023-01-17"
output: 
 prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# Working with matrices, lists, and data frames

### 1. Assign to the variable n_dims a single random integer between 3 and 10.
  + Create a vector of consecutive integers from 1 to n_dims2.
  
```{r}
set.seed(100)
n_dims = sample(3:10, 1)
myVec = c(1:(n_dims)^2)
print(myVec)
```
  + Use the sample function to randomly reshuffle these values.
```{r}
rVec <- sample(myVec)
print(rVec)
```
  + Create a square matrix with these elements.
```{r}
mMat <- matrix(data=rVec, nrow=n_dims, ncol=n_dims)
print(mMat)
```
  + Find a function in r to transpose the matrix.
```{r}
tmMat <- t(mMat)
print(tmMat)
```
  + Calculate the sum and the mean of the elements in the first row and then the last row.
```{r}
# first row
mean(tmMat[1,])
sum(tmMat[1,])

# last row
mean(tmMat[n_dims,])
sum(tmMat[n_dims,])
```
### 2. Create a list with the following named elements:
  + `my_matrix`, which is a 4 x 4 matrix filled with random uniform values
  + `my_logical` which is a 100-element vector of TRUE or FALSE values. You can do this efficiently by setting up a vector of random values and then applying an inequality to it.
  + `my_letters`, which is a 26-element vector of all the lower-case letters in random order.
```{r}
set.seed(1000)

my_list <- list(my_matrix = matrix(data = runif(16), nrow = 4, ncol = 4), my_logical = (runif(100, 0, 10)) > 5, my_letters = sample(letters[1:26]))
print(my_list)
```
  + create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.
  + use the typeof() function to confirm the underlying data types of each component in this list
  + combine the underlying elements from the new list into a single atomic vector with the c() function.
  + what is the data type of this vector?
```{r}

my_list2 <- list(my_list$my_matrix[2,2], my_list$my_logical[2], my_list$my_letters[2])
print(my_list2)
str(my_list2)

a_vec <- unlist(my_list2)
print(a_vec)
typeof(a_vec)
```
### 3. Create an empty data frame with two variables (= columns) and 26 observations (= rows) below:
```{r}
dFrame1 <- data.frame(rep(0,26), rep(0,26))
print(dFrame1)
```
  + call the first column/variable my_unifs and fill it with 26 random uniform values from 0 to 10
  + call the second variable my_letters and fill it with 26 capital letters in random order.
```{r}
set.seed(1000)
colnames(dFrame1) <- c("my_unifs", "my_letters")

dFrame1$my_unifs <- runif(26, 0, 10)
dFrame1$my_letters <- sample(LETTERS[1:26])
print(dFrame1)
```
  + for the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.
```{r}
set.seed(1000)
dFrame1$my_unifs[sample(1:26, 4)] <- NA
print(dFrame1)
```
  + for the first variable, write a single line of R code to identify which rows have the missing values.
re-order the entire data frame to arrange the second variable in alphabetical order.
```{r}
which(is.na(dFrame1$my_unifs))

dFrame1 <- dFrame1[order(dFrame1$my_letters),]
print(dFrame1)
```
  + calculate the column mean for the first variable.
```{r}
mean(dFrame1$my_unifs, na.rm=T)
```
  + rename the second column ‘my_LETTERS’
```{r}
colnames(dFrame1)[2] <- "my_LETTERS"
print(dFrame1)
```