---
title: "Assignment 8"
author: "Ben Merz"
date: "2023-01-26"
output:
  prettydoc::html_pretty:
  theme: cayman
  highlight: github
---
# Code Reflection

1. Go through your recent assignments and the posted solutions (Assignment 6 posted solutions and Weekly Assignment 2 solutions) - compare your code to the posted code.
  * Can you run your simulated data function with new values for the means? If not, what do you need to change about your code?
  * Are there differences between the posted code and yours? Did you notice you were missing anything?
  * Make sure you annotate your code using # and leave brief descriptions of your thought process.

For assignment 6, I just annotated my previous [code](Assignment_6.html)

```{r}
### Orginial Code



set.seed(1000)
########################
# Function: dataFCT
# Creates a simulated two column data frame where the values means can be chosen
# input: numeric values of two means and their associated standard deviations
# output: a two column data frame with the first twenty five values being Control and the second twenty five being of treatment
# --------------------------------------------------------
dataFCT <- function(m1 = 10, sd1 = 1.5, m2 = 45, sd2 = 2){
  dFrame <- data.frame(
    Type = rep(c("Control", "Treatment"), each = 25),
    Value = c(rnorm(25, m1, sd1), rnorm(25, m2, sd2))
  )
  return(dFrame)
}

########################
# Function: pFunc 
# Displays only the p-value from a one way annova test of a two column data frame
# input: Any two column data frame
# output: The associated p-value for a one way annova test of that data frame.
# --------------------------------------------------------

pFunc <- function(d = data_output){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}
```


```{r}
### Annoatated code


set.seed(1000)
########################
# Function: dataFCT
# Creates a simulated two column data frame where the values means can be chosen
# input: numeric values of two means and their associated standard deviations
# output: a two column data frame with the first twenty five values being Control and the second twenty five being of treatment
# --------------------------------------------------------
dataFCT <- function(m1 = 10, sd1 = 1.5, m2 = 45, sd2 = 2, n = 25){
  dFrame <- data.frame(
    Type = rep(c("Control", "Treatment"), each = n),
    Value = c(rnorm(n, m1, sd1), rnorm(n, m2, sd2))
  )
  return(dFrame)
}

dataFCT()
dataFCT(m1 = 12, sd1 = 1.7, m2 = 73, sd2 = 3, n = 30)

# I can run my simulated data function with new values for the means
# However I did not add the ability to change the sample size.
# Replacing the count in each r norm function is more elegant since it's a repeated value.
# It also makes this function more applicable to other cases




########################
# Function: pFunc 
# Displays only the p-value from a one way annova test of a two column data frame
# input: Any two column data frame
# output: The associated p-value for a one way annova test of that data frame.
# --------------------------------------------------------

pFunc <- function(d = NULL){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}

# My default input I set as the variable I used to store the default output of my data function
# This is problematic because it links pFunc to dataFCT. Setting the default data to null removes this.
# I prefer the way that I extract the data by column instead of name. Column names can change.

pFunc(dataFCT())
```

