---
title: "Assignment 9"
author: "Ben Merz"
date: "2023-01-30"
output:
  prettydoc::html_pretty:
  theme: cayman
  highlight: github
---
1. Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}

v1 <- sample(c(0:7), size = 150, replace = T)
counter <- 0

zeroCount <- for(i in v1){
  if(i == 0){counter <- counter + 1}
}

print(counter)


```

2. Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}

##################################################
# FUNCTION: matrix_gen
# generates matrix of specified dimensions 
# inputs: the rows (r) and the colums (c) of the desired matrix
# outputs: matrix of r x c dimension where each element is the product of the row number x the column number
#------------------------------------------------- 
matrix_gen <- function(r = NULL, c = NULL){
  mat <- matrix(NA, nrow = r, ncol = c)
  for (i in 1:nrow(mat)) {
    for (j in 1:ncol(mat)) {
      mat[i,j] <- i * j
    } # end of column j loop
  } # end or row i loop
  return(mat)
}

matrix_gen(5, 6)
  
  

```

3. Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}



```



