---
title: "Assignment 9"
author: "Ben Merz"
date: "2023-01-30"
output:
  prettydoc::html_pretty:
  theme: cayman
  highlight: github
---
1. Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}

v1 <- sample(c(0:7), size = 150, replace = T)
counter <- 0

zeroCount <- for(i in v1){
  if(i == 0){counter <- counter + 1}
}

print(counter)


```

2. Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}
##################################################
# FUNCTION: matrix_gen
# generates matrix of specified dimensions 
# inputs: the rows (r) and the colums (c) of the desired matrix
# outputs: matrix of r x c dimension where each element is the product of the row number x the column number
#------------------------------------------------- 
matrix_gen <- function(r = NULL, c = NULL){
  mat <- matrix(NA, nrow = r, ncol = c)
  for (i in 1:nrow(mat)) {
    for (j in 1:ncol(mat)) {
      mat[i,j] <- i * j
    } # end of column j loop
  } # end or row i loop
  return(mat)
}

matrix_gen(5, 6)
  
  

```

3. Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}
########################
# Function: dataFCT
# Creates a simulated two column data frame where the values means can be chosen
# input: numeric values of two means and their associated standard deviations
# output: a two column data frame with the first twenty five values being Control and the second twenty five being of treatment
# --------------------------------------------------------
dataFCT <- function(m1 = 10, sd1 = 1.5, m2 = 45, sd2 = 2, n = 25){
  dFrame <- data.frame(
    Type = rep(c("Control", "Treatment"), each = n),
    Value = c(rnorm(n, m1, sd1), rnorm(n, m2, sd2))
  )
  return(dFrame)
}

########################
# Function: pFunc 
# Displays only the p-value from a one way annova test of a two column data frame
# input: Any two column data frame
# output: The associated p-value for a one way annova test of that data frame.
# --------------------------------------------------------

pFunc <- function(d = NULL){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}


########################
# Function: df_func 
# creates a 1 column data frame of some length (rows) that fills in each value with a random p-value from the pFunc and dataFCT functions
# input: a list of numbers from 1:n
# output: a dataframe with n rows
# --------------------------------------------------------

df_func <- function(rows = 1:100){
  df <- data.frame(x = rows)
  colnames(df) <- "p-values"
  for(i in rows){
   df[i, ] <- pFunc(dataFCT())
  }
  return(df)
}

df_func()
```



