---
title: "Assignment 8"
author: "Ben Merz"
date: "2023-01-26"
output:
  prettydoc::html_pretty:
  theme: cayman
  highlight: github
---
# Code Reflection

1. Go through your recent assignments and the posted solutions (Assignment 6 posted solutions and Weekly Assignment 2 solutions) - compare your code to the posted code.
  * Can you run your simulated data function with new values for the means? If not, what do you need to change about your code?
  * Are there differences between the posted code and yours? Did you notice you were missing anything?
  * Make sure you annotate your code using # and leave brief descriptions of your thought process.

For assignment 6, I just annotated my previous [code](Assignment_6.html)

```{r}
### Orginial Code



set.seed(1000)
########################
# Function: dataFCT
# Creates a simulated two column data frame where the values means can be chosen
# input: numeric values of two means and their associated standard deviations
# output: a two column data frame with the first twenty five values being Control and the second twenty five being of treatment
# --------------------------------------------------------
dataFCT <- function(m1 = 10, sd1 = 1.5, m2 = 45, sd2 = 2){
  dFrame <- data.frame(
    Type = rep(c("Control", "Treatment"), each = 25),
    Value = c(rnorm(25, m1, sd1), rnorm(25, m2, sd2))
  )
  return(dFrame)
}

########################
# Function: pFunc 
# Displays only the p-value from a one way annova test of a two column data frame
# input: Any two column data frame
# output: The associated p-value for a one way annova test of that data frame.
# --------------------------------------------------------

pFunc <- function(d = data_output){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}
```


```{r}
### Annoatated code


set.seed(1000)
########################
# Function: dataFCT
# Creates a simulated two column data frame where the values means can be chosen
# input: numeric values of two means and their associated standard deviations
# output: a two column data frame with the first twenty five values being Control and the second twenty five being of treatment
# --------------------------------------------------------
dataFCT <- function(m1 = 10, sd1 = 1.5, m2 = 45, sd2 = 2, n = 25){
  dFrame <- data.frame(
    Type = rep(c("Control", "Treatment"), each = n),
    Value = c(rnorm(n, m1, sd1), rnorm(n, m2, sd2))
  )
  return(dFrame)
}

dataFCT()
dataFCT(m1 = 12, sd1 = 1.7, m2 = 73, sd2 = 3, n = 30)

# I can run my simulated data function with new values for the means
# However I did not add the ability to change the sample size.
# Replacing the count in each r norm function is more elegant since it's a repeated value.
# It also makes this function more applicable to other cases




########################
# Function: pFunc 
# Displays only the p-value from a one way annova test of a two column data frame
# input: Any two column data frame
# output: The associated p-value for a one way annova test of that data frame.
# --------------------------------------------------------

pFunc <- function(d = NULL){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}

# My default input I set as the variable I used to store the default output of my data function
# This is problematic because it links pFunc to dataFCT. Setting the default data to null removes this.
# I prefer the way that I extract the data by column instead of name. Column names can change.

pFunc(dataFCT())
```

2. I used dryad data to reconstruct a publication-quality figure. Copy my code into an Rmd file and annotate what each ggplot line of code is doing, including any arguments. You can use a combination of googling and ‘trial/error coding:’ change the arguments/options to visually see how it affects the plot.

```{r message=FALSE, warning=FALSE}
# Load in packages
library(tidyverse)
library(ggthemes)

# Load in data set for analysis and new graph
dryadData <- read.table("/Users/BenM/Library/Mobile Documents/com~apple~CloudDocs/Documents/College/Bio/Reproducible R/Git Repository/BIOL1007A/Data/d_8/veysey-babbitt_data_amphibian.csv", header=TRUE, sep=",", stringsAsFactors = TRUE)

# Setting the species of RASY and AMMA as factor with two levels(the abreviations common name)
dryadData$species<-factor(dryadData$species, labels=c("Spotted Salamander", "Wood Frog")) #creating 'labels' to use for the plot
class(dryadData$treatment)

# Setting treatment as a factor with three levels(the diferent reference distance)
dryadData$treatment <- factor(dryadData$treatment,
                              levels=c("Reference",
                                       "100m", "30m"))


p<- ggplot(data=dryadData, 
           aes(x=interaction(wetland, treatment), # 
               y=count.total.adults, # y value equal to the total number of adults
               fill=factor(year))) + # set the color to change via year
  geom_bar(position="dodge", # makes the graphs appear vertical to eachother
          stat="identity", # use the y values as the y axis
           color="black") + # outise border of bar graph is black
  ylab("Number of breeding adults") + # label the y axis
  xlab("") + # no label on x axis
  scale_y_continuous(breaks = c(0,100,200,300,400,500)) + # y axis should be broken up by 100s continyally
  scale_x_discrete(labels=c("30 (Ref)", "124 (Ref)", "141 (Ref)", "25 (100m)","39 (100m)","55 (100m)","129 (100m)", "7 (30m)","19 (30m)","20 (30m)","59 (30m)")) +# discrete labels broken up with the references
  facet_wrap(~species, nrow=2, strip.position="right") + # breaks the graph into two instead of overalying each on top of eachother
  
  # setting colors and style
  theme_few() + scale_fill_grey() + 
  theme(panel.background = element_rect(fill = 'gray94', color = 'black'), legend.position="top",  legend.title= element_blank(), axis.title.y = element_text(size=12, face="bold", colour = "black"), strip.text.y = element_text(size = 10, face="bold", colour = "black")) + 
  
   guides(fill=guide_legend(nrow=1,byrow=TRUE)) # need for the legend to be vertical instead of horizontal

p
```


